Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-18 code/analysis.Rmd
resized plot
a couple changes to r code

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_point(size = 2, pch = 4) +
  theme_bw() +
  labs(x = expression(phi[c]), color = "Study") +
  scale_color_manual(values = c("darkgreen","red")) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi^-1.41")

ggsave("../pics/cphiplot.png",cplot,dpi = 600)

>>>>

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_point(size = 2, pch = 4) +
  theme_bw() +
  labs(x = expression(phi[c]), color = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi[c]^-1.41")

ggsave("../pics/cphiplot.png",cplot,dpi = 600, height = 4, units = "in")
